---
title: "Week 1 Exercises"
author: "Hayley Morway"
date: "March 18, 2023"
output: pdf_document
---

Please complete all exercises below WITHOUT using any libraries/packages.

# Exercise 1
Assign 10 to the variable x. Assign 5 to the variable y. Assign 20 to the variable z.

```{r ex1}
#assign values to variables
x <- 10
y <- 5
z <- 20

```


# Exercise 2
Show that x is less than z but greater than y.

**Note: your output must be a SINGLE boolean, do not output a boolean for each expression.**

```{r ex2}
#x less than z and greater than y
(x < z) & (y < x)
```

# Exercise 3
Show that x and y do not equal z. 

**Note: your output must be a SINGLE boolean, do not output a boolean for each expression.**

```{r ex3}
#x not equal to z and y not equal to z
(x != z) & (y != z)
```


# Exercise 4
Show that the formula `x + 2y = z`. 

**Note: your output must be a SINGLE boolean**

```{r ex4}
#x plus 2 times y is equal to z
(x + 2*y) == z
```

# Exercise 5
I have created a vector (test_vector) of integers for you. Determine if any of x, y, or z are in the vector. 

**Note: your output must be a SINGLE boolean, do not output a boolean for each expression.**


```{r ex5}
test_vector <- c(1,5,11:22)
#x in test vector or y in test vector or z in test vector
(x %in% test_vector) | (y %in% test_vector) | (z %in% test_vector)
#####any((x %in% test_vector), (y %in% test_vector), (z %in% test_vector))
```

# Exercise 6
Show which value is contained in the test vector. To do this you will need to create an element-wise logical vector using operators. `x == vector`. Once you have done that you will need to use slicing to return all indices that have matches.
**Note: your output should be two integers**

```{r ex6}
#create indices variable to store x equal to test vector or y equal 
#to test vector or z equal to test vector
indices <- (x == test_vector) | (y == test_vector) | (z == test_vector)
#slice test vector for those values contained in indices variable
test_vector[indices]
####test_vector[(x == test_vector) | y == test_vector) | z == test_vector)]
```

